\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2012-02-03 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
MSnSet combine method and related updates/changes
CHANGES IN VERSION 1.3.8
-------------------------
 o Modified trimMz warning to report acquisition number <2012-02-01 Wed>
 o add 'experimentData(object, value) <- ' method for signature eSet
   and MIAPE <2012-02-02 Thu>
 o combine methods for MIAPE instances <2012-02-02 Thu>
 o combine methods for MSnProcess instances <2012-02-02 Thu>
 o changed qual drop warning into message in combineFeatures,
   updated test_MSnSet accordingly <2012-02-02 Thu>
 o new updateFvarLabels and updateSampleNames function <2012-02-03 Fri>
 o combine method for MS

\begin{figure}[p]
<<quantitation-plot,fig=T,echo=F,tikz=T,external=F,width=5,height=5>>=
grid.newpage()
pushViewport(viewport(layout = grid.layout(2, 2)))
vplayout <- function(x, y)
  viewport(layout.pos.row = x, layout.pos.col = y)
print(p + opts(title = "Quantitation using 'sum'") +
      geom_point(size = 3, alpha = I(1/3), colour = "red"),
      vp = vplayout(1, 1))
print(p + opts(title = "Quantitation using 'max'") +
      geom_point(aes(x = 114.1, y = 3), alpha = I(1/3), colour = "red", size = 3),
      vp = vplayout(1, 2))
print(p +
      opts(title = "Trapezoidation and strict=FALSE") +
      geom_polygon(alpha = I(1/5), fill = "red"),
      vp = vplayout(2, 1))
print(p +
      opts(title = "Trapezoidation and strict=TRUE") + 
      geom_polygon(aes(x = c(NA, 114.05, 114.05, 114.1, 114.15, 114.15, NA),
                       y=c(NA, 0, 1, 3, 1, 0, NA)), fill = "red", alpha = I(1/5)),
      vp = vplayout(2,2))
@ 
\caption{The different quantitation methods are illustrated above. 
  Quantitation using \Robject{sum} sums all the data points in the peaks to 
  produce, for this example, \Sexpr{quantify(ssp,iTRAQ4[1],method="sum")[[1]]}, 
  whereas method \Robject{max} only uses the peak's maximum intensity, 
  \Sexpr{quantify(ssp,iTRAQ4[1],method="max")[[1]]}. 
  \Robject{Trapezoidation} calculates the area under the peak taking 
  the full with into account (using \Robject{strict=FALSE} gives
  \Sexpr{round(quantify(ssp,iTRAQ4[1],method="trap",strict=FALSE)[[1]],3)}) 
  or only the width as defined by the reporter 
  (using \Robject{strict=TRUE} gives
  \Sexpr{round(quantify(ssp,iTRAQ4[1],method="trap",strict=TRUE)[[1]],3)}). }
\label{fig:quant-methods}
\end{figure}

>>>>

\begin{figure}[p]
<<quantitation-plot,fig=T,echo=F,tikz=T,external=F,width=5,height=5>>=
grid.newpage()
pushViewport(viewport(layout = grid.layout(2, 2)))
vplayout <- function(x, y)
  viewport(layout.pos.row = x, layout.pos.col = y)
print(p + opts(title = "Quantitation using 'sum'") +
      geom_point(size = 3, alpha = I(1/3), colour = "red"),
      vp = vplayout(1, 1))
print(p + opts(title = "Quantitation using 'max'") +
      geom_point(aes(x = 114.1, y = 3),
                 alpha = I(1/18),
                 colour = "red", size = 3),
      vp = vplayout(1, 2))
print(p +
      opts(title = "Trapezoidation and strict=FALSE") +
      geom_polygon(alpha = I(1/5), fill = "red"),
      vp = vplayout(2, 1))
print(p +
      opts(title = "Trapezoidation and strict=TRUE") + 
      geom_polygon(aes(x = c(NA, 114.05, 114.05, 114.1, 114.15, 114.15, NA),
                       y=c(NA, 0, 1, 3, 1, 0, NA)), fill = "red", alpha = I(1/5)),
      vp = vplayout(2,2))

@ 
\caption{The different quantitation methods are illustrated above. 
  Quantitation using \Robject{sum} sums all the data points in the peaks to 
  produce, for this example, \Sexpr{quantify(ssp,iTRAQ4[1],method="sum")[[1]]}, 
  whereas method \Robject{max} only uses the peak's maximum intensity, 
  \Sexpr{quantify(ssp,iTRAQ4[1],method="max")[[1]]}. 
  \Robject{Trapezoidation} calculates the area under the peak taking 
  the full with into account (using \Robject{strict=FALSE} gives
  \Sexpr{round(quantify(ssp,iTRAQ4[1],method="trap",strict=FALSE)[[1]],3)}) 
  or only the width as defined by the reporter 
  (using \Robject{strict=TRUE} gives
  \Sexpr{round(quantify(ssp,iTRAQ4[1],method="trap",strict=TRUE)[[1]],3)}). }
\label{fig:quant-methods}
\end{figure}
